---
title: "pesticide_risk_plots"
author: "Joe Collins"
date: "`r Sys.Date()`"
output: pdf_document
---

# Pesticide Risk Plots


Set the working directory and load the necessary packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# # Set the root directory for the R Markdown file
# knitr::opts_knit$set(root.dir = "~/OneDrive - Harper Adams University/Data/agronomy/")


# PACKAGES ####

library(dplyr)
library(purrr) # For list filtering
library(stringr) # replace characters
library(ggplot2) # plotting 
library(tidyr)
library(ggpubr)
```




# Data 

Read the combined data set

```{r load data}
#combined_dat <- read.csv(file = "data/pesticide_data/pesticide_properties_data.csv")

# source(file = "~/Documents/GitHub/pesticide_info_web_scraper/pesticide_risk_summary_stats.R")


dat <- read.csv(file = "sym_link_pesticide_data/data/pesticide_data/danish_pli_total_pli_data.csv")

dat$year <- factor(dat$year, levels = c(2022, 2023, 2024))

dat$treatment <- factor(dat$treatment, levels = c("Conservation", "Conventional"))

```





#________________________________
# Plots by year

# ~ Total PLI x rate


```{r Total PLI plots}

sum <- 
   dat %>%
  group_by(year, treatment) %>%
  summarise(
    n = n(),
    sum = round(x = sum(total_pli_x_rate, na.rm = TRUE), digits = 2)
  )


p1 <-
ggplot(data = sum, 
            aes(x = treatment, 
                y = sum, 
                fill = treatment)) +
geom_bar(stat = "identity", 
           color = "black", 
           position = "dodge") + 
  labs(
    subtitle = "Total PLI", 
    x = "Treatment",
    y = "PLI") +
  theme_bw() +
  scale_fill_manual(values=c("turquoise3","tomato2"), 
                    name = "Treatment") +
  theme(strip.text.x = element_text(size = 12, 
                                    color = "black", 
                                    face = "bold.italic"), 
        legend.position = "bottom", 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank()) +
  facet_wrap(~ year, 
             ncol = 4, 
             scales = 'free_x') 

p1

```



# ~ Ecotoxicity PLI x rate


```{r ecotox pli plots}

names(dat)

sum <- 
   dat %>%
  group_by(year, treatment) %>%
  summarise(
    n = n(),
    sum = round(x = sum(ecotox_indic_x_rate, na.rm = TRUE), digits = 2)
  )


p2 <-
ggplot(data = sum, 
            aes(x = treatment, 
                y = sum, 
                fill = treatment)) +
geom_bar(stat = "identity", 
           color = "black", 
           position = "dodge") + 
  labs(
    subtitle = "Ecotoxicity", 
    x = "Treatment",
    y = "PLI") +
  theme_bw() +
  scale_fill_manual(values=c("turquoise3","tomato2"), 
                    name = "Treatment") +
  theme(strip.text.x = element_text(size = 12, 
                                    color = "black", 
                                    face = "bold.italic"), 
        legend.position = "bottom", 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank()) +
  facet_wrap(~ year, 
             ncol = 4, 
             scales = 'free_x') 

p2

```




# ~ Environmental fate PLI x rate


```{r env fate pli plots}

names(dat)

sum <- 
   dat %>%
  group_by(year, treatment) %>%
  summarise(
    n = n(),
    sum = round(x = sum(env_fate_indic_x_rate, na.rm = TRUE), digits = 2)
  )


p3 <-
ggplot(data = sum, 
            aes(x = treatment, 
                y = sum, 
                fill = treatment)) +
geom_bar(stat = "identity", 
           color = "black", 
           position = "dodge") + 
  labs(
    subtitle = "Environmental fate", 
    x = "Treatment",
    y = "PLI") +
  theme_bw() +
  scale_fill_manual(values=c("turquoise3","tomato2"), 
                    name = "Treatment") +
  theme(strip.text.x = element_text(size = 12, 
                                    color = "black", 
                                    face = "bold.italic"), 
        legend.position = "bottom", 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank()) +
  facet_wrap(~ year, 
             ncol = 4, 
             scales = 'free_x') 

p3

```




# ~ Human health PLI x rate


```{r human health pli plots}

names(dat)

sum <- 
   dat %>%
  group_by(year, treatment) %>%
  summarise(
    n = n(),
    sum = round(x = sum(human_health_indic_x_rate, na.rm = TRUE), digits = 2)
  )


p4 <-
ggplot(data = sum, 
            aes(x = treatment, 
                y = sum, 
                fill = treatment)) +
geom_bar(stat = "identity", 
           color = "black", 
           position = "dodge") + 
  labs(
    subtitle = "Human Health", 
    x = "Treatment",
    y = "PLI") +
  theme_bw() +
  scale_fill_manual(values=c("turquoise3","tomato2"), 
                    name = "Treatment") +
  theme(strip.text.x = element_text(size = 12, 
                                    color = "black", 
                                    face = "bold.italic"), 
        legend.position = "bottom", 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank()) +
  facet_wrap(~ year, 
             ncol = 4, 
             scales = 'free_x') 

p4

```



# ~ Total mass PLI x rate


```{r total ppp mass plots}

names(dat)

sum <- 
   dat %>%
  group_by(year, treatment) %>%
  summarise(
    n = n(),
    sum = round(x = sum(avg_normalized_rate_kg_ha, na.rm = TRUE), digits = 2)
  )


p5 <-
ggplot(data = sum, 
            aes(x = treatment, 
                y = sum, 
                fill = treatment)) +
geom_bar(stat = "identity", 
           color = "black", 
           position = "dodge") + 
  labs(
    y = expression("Total mass (kg"~"ha"^{-1}~")"), 
    x = "Treatment",
    subtitle = "Total mass"
    ) +
  theme_bw() +
  scale_fill_manual(values=c("turquoise3","tomato2"), 
                    name = "Treatment") +
  theme(strip.text.x = element_text(size = 12, 
                                    color = "black", 
                                    face = "bold.italic"), 
        legend.position = "bottom", 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank()) +
  facet_wrap(~ year, 
             ncol = 4, 
             scales = 'free_x') 

p5

```

# joint plot 


```{r joint plot xyt}

ggarrange(p2,p3,p4,p5,p1, 
          ncol = 3, 
          nrow = 2, 
          labels = c("A","B","C","D","E"), 
          common.legend = TRUE, legend = "bottom")

```

```{r}

ggsave(filename = "sym_link_pesticide_data/plots/pesticide_risk_plots/danish_pli_join_plot.png",
       width = 10, height = 6)

```






#________________________________
# Plots by treatment

# ~ Total PLI x rate


```{r Total PLI xt plots}

sum <- 
   dat %>%
  group_by(treatment, year) %>%
  summarise(
    n = n(),
    sum = round(x = sum(total_pli_x_rate, na.rm = TRUE), digits = 2)
  ) %>% 
  group_by(treatment) %>%
  summarise(
    n = n(),
    # sum = round(sum(total_pli_x_rate, na.rm = TRUE), 2),
    mean = round(mean(sum, na.rm = TRUE), 2),
    sd = round(sd(sum, na.rm = TRUE), 2),
    se = round(sd(sum, na.rm = TRUE) / sqrt(n), 2) # Standard Error
  )
  
sum


p1 <-
ggplot(data = sum, 
            aes(x = treatment, 
                y = mean, 
                fill = treatment)) +
geom_bar(stat = "identity", 
           color = "black", 
           position = "dodge") + 
  labs(
    subtitle = "Total PLI", 
    x = "Treatment",
    y = "PLI") +
  theme_bw() +
  scale_fill_manual(values=c("turquoise3","tomato2"), 
                    name = "Treatment") +
      geom_errorbar(aes(ymin=mean-se,
                        ymax=mean+se),
                    width=.2,                    # Width of the error bars
                    position=position_dodge(.9)) +
  theme(strip.text.x = element_text(size = 12, 
                                    color = "black", 
                                    face = "bold.italic"), 
        legend.position = "bottom", 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank()) 

p1

```



# ~ Ecotoxicity PLI x rate


```{r ecotox pli xt plots}

sum <- 
   dat %>%
  group_by(treatment, year) %>%
  summarise(
    n = n(),
    sum = round(x = sum(ecotox_indic_x_rate, na.rm = TRUE), digits = 2)
  ) %>% 
  group_by(treatment) %>%
  summarise(
    n = n(),
    # sum = round(sum(total_pli_x_rate, na.rm = TRUE), 2),
    mean = round(mean(sum, na.rm = TRUE), 2),
    sd = round(sd(sum, na.rm = TRUE), 2),
    se = round(sd(sum, na.rm = TRUE) / sqrt(n), 2) # Standard Error
  )

sum

p2 <-
ggplot(data = sum, 
            aes(x = treatment, 
                y = mean, 
                fill = treatment)) +
geom_bar(stat = "identity", 
           color = "black", 
           position = "dodge") + 
  labs(
    subtitle = "Ecotoxicity", 
    x = "Treatment",
    y = "PLI") +
  theme_bw() +
  scale_fill_manual(values=c("turquoise3","tomato2"), 
                    name = "Treatment") +
        geom_errorbar(aes(ymin=mean-se,
                        ymax=mean+se),
                    width=.2,                    # Width of the error bars
                    position=position_dodge(.9)) +
  theme(strip.text.x = element_text(size = 12, 
                                    color = "black", 
                                    face = "bold.italic"), 
        legend.position = "bottom", 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank()) 

p2

```




# ~ Environmental fate PLI x rate


```{r env fate pli xt plots}


sum <- 
   dat %>%
  group_by(treatment, year) %>%
  summarise(
    n = n(),
    sum = round(x = sum(env_fate_indic_x_rate, na.rm = TRUE), digits = 2)
  ) %>% 
  group_by(treatment) %>%
  summarise(
    n = n(),
    # sum = round(sum(total_pli_x_rate, na.rm = TRUE), 2),
    mean = round(mean(sum, na.rm = TRUE), 2),
    sd = round(sd(sum, na.rm = TRUE), 2),
    se = round(sd(sum, na.rm = TRUE) / sqrt(n), 2) # Standard Error
  )

sum

p3 <-
ggplot(data = sum, 
            aes(x = treatment, 
                y = mean, 
                fill = treatment)) +
geom_bar(stat = "identity", 
           color = "black", 
           position = "dodge") + 
  labs(
    subtitle = "Environmental fate", 
    x = "Treatment",
    y = "PLI") +
  theme_bw() +
  scale_fill_manual(values=c("turquoise3","tomato2"), 
                    name = "Treatment") +
   geom_errorbar(aes(ymin=mean-se,
                        ymax=mean+se),
                    width=.2,                    # Width of the error bars
                    position=position_dodge(.9)) +
  theme(strip.text.x = element_text(size = 12, 
                                    color = "black", 
                                    face = "bold.italic"), 
        legend.position = "bottom", 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank()) 

p3

```




# ~ Human health PLI x rate


```{r human health pli xt plots}

names(dat)

# sum <- 
#    dat %>%
#   group_by(treatment) %>%
#   summarise(
#     n = n(),
#     sum = round(x = sum(human_health_indic_x_rate, na.rm = TRUE), digits = 2)
#   )

sum <- 
   dat %>%
  group_by(treatment, year) %>%
  summarise(
    n = n(),
    sum = round(x = sum(human_health_indic_x_rate, na.rm = TRUE), digits = 2)
  ) %>% 
  group_by(treatment) %>%
  summarise(
    n = n(),
    # sum = round(sum(total_pli_x_rate, na.rm = TRUE), 2),
    mean = round(mean(sum, na.rm = TRUE), 2),
    sd = round(sd(sum, na.rm = TRUE), 2),
    se = round(sd(sum, na.rm = TRUE) / sqrt(n), 2) # Standard Error
  )


p4 <-
ggplot(data = sum, 
            aes(x = treatment, 
                y = mean, 
                fill = treatment)) +
geom_bar(stat = "identity", 
           color = "black", 
           position = "dodge") + 
  labs(
    subtitle = "Human Health", 
    x = "Treatment",
    y = "PLI") +
  theme_bw() +
  scale_fill_manual(values=c("turquoise3","tomato2"), 
                    name = "Treatment") +
   geom_errorbar(aes(ymin=mean-se,
                        ymax=mean+se),
                    width=.2,                    # Width of the error bars
                    position=position_dodge(.9)) +
  theme(strip.text.x = element_text(size = 12, 
                                    color = "black", 
                                    face = "bold.italic"), 
        legend.position = "bottom", 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank()) 

p4

```



# ~ Total mass PLI x rate


```{r total ppp mass xt plots}

names(dat)

# sum <- 
#    dat %>%
#   group_by(treatment) %>%
#   summarise(
#     n = n(),
#     sum = round(x = sum(avg_normalized_rate_kg_ha, na.rm = TRUE), digits = 2)
#   )


sum <- 
   dat %>%
  group_by(treatment, year) %>%
  summarise(
    n = n(),
    sum = round(x = sum(avg_normalized_rate_kg_ha, na.rm = TRUE), digits = 2)
  ) %>% 
  group_by(treatment) %>%
  summarise(
    n = n(),
    # sum = round(sum(total_pli_x_rate, na.rm = TRUE), 2),
    mean = round(mean(sum, na.rm = TRUE), 2),
    sd = round(sd(sum, na.rm = TRUE), 2),
    se = round(sd(sum, na.rm = TRUE) / sqrt(n), 2) # Standard Error
  )



p5 <-
ggplot(data = sum, 
            aes(x = treatment, 
                y = mean, 
                fill = treatment)) +
geom_bar(stat = "identity", 
           color = "black", 
           position = "dodge") + 
  labs(
    subtitle = "Total mass", 
    x = "Treatment",
    y = expression("Total mass (kg"~"ha"^{-1}~")")) +
  theme_bw() +
  scale_fill_manual(values=c("turquoise3","tomato2"), 
                    name = "Treatment") +
   geom_errorbar(aes(ymin=mean-se,
                        ymax=mean+se),
                    width=.2,                    # Width of the error bars
                    position=position_dodge(.9)) +
  theme(strip.text.x = element_text(size = 12, 
                                    color = "black", 
                                    face = "bold.italic"), 
        legend.position = "bottom", 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank()) 

p5

```

# joint plot 


```{r joint xt plot xt}

ggarrange(p2,p3,p4,p5,p1, 
          ncol = 5, 
          nrow = 1, 
          labels = c("A","B","C","D","E"), 
          common.legend = TRUE, legend = "bottom")

```

```{r}

ggsave(filename = "sym_link_pesticide_data/plots/pesticide_risk_plots/danish_pli_treatment_joint_plot.png",
       width = 10, height = 3.5)

```






#______________________________
# Proportions 



# ~ application rates 
```{r}

# Summarize total usage by category and treatment
category_summary <- dat %>%
  group_by(treatment, category) %>%  # Group by both treatment and category
  summarise(total_usage = sum(avg_normalized_rate_kg_ha, na.rm = TRUE), .groups = "drop") %>%
  group_by(treatment) %>%  # Group again by treatment to calculate proportions correctly
  mutate(percentage = (total_usage / sum(total_usage)) * 100) %>%
  ungroup()

category_summary

a <-
ggplot(category_summary, aes(x = treatment, y = percentage, fill = category)) +
  geom_col(position = "stack") +  # Stacked bars
  scale_fill_brewer(palette = "Set1") +  # Change to any Brewer palette
  labs(subtitle = "Total Mass",
       x = "Treatment",
       y = "Proportion (%)",
       fill = "Pesticide Category") +
  theme_minimal()

a


```


# ~ total PLI
```{r}

# Summarize total usage by category and treatment
category_summary <- dat %>%
  group_by(treatment, category) %>%  # Group by both treatment and category
  summarise(total_x = sum(total_pli, na.rm = TRUE), .groups = "drop") %>%
  group_by(treatment) %>%  # Group again by treatment to calculate proportions correctly
  mutate(percentage = (total_x / sum(total_x)) * 100) %>%
  ungroup()

category_summary


b <-
ggplot(category_summary, 
       aes(x = treatment, 
           y = percentage, 
           fill = category)) +
  geom_col(position = "stack") +  # Stacked bars
  scale_fill_brewer(palette = "Set1") +  # Change to any Brewer palette
  labs(subtitle = "Total PLI",
       x = "Treatment",
       y = "Proportion (%)",
       fill = "Pesticide Category") +
  theme_minimal()


b

```


# ~ ecotoxicity PLI
```{r}

# Summarize total usage by category and treatment
category_summary <- dat %>%
  group_by(treatment, category) %>%  # Group by both treatment and category
  summarise(total_x = sum(EcoTox_Indicator, na.rm = TRUE), .groups = "drop") %>%
  group_by(treatment) %>%  # Group again by treatment to calculate proportions correctly
  mutate(percentage = (total_x / sum(total_x)) * 100) %>%
  ungroup()

category_summary

c <-
ggplot(category_summary, 
       aes(x = treatment, 
           y = percentage, 
           fill = category)) +
  geom_col(position = "stack") +  # Stacked bars
  scale_fill_brewer(palette = "Set1") +  # Change to any Brewer palette
  labs(subtitle = "Ecotoxicity",
       x = "Treatment",
       y = "Proportion (%)",
       fill = "Pesticide Category") +
  theme_minimal()


c

```



# ~ environmental fate PLI
```{r}

# Summarize total usage by category and treatment
category_summary <- dat %>%
  group_by(treatment, category) %>%  # Group by both treatment and category
  summarise(total_x = sum(Env_Fate_Indicator, na.rm = TRUE), .groups = "drop") %>%
  group_by(treatment) %>%  # Group again by treatment to calculate proportions correctly
  mutate(percentage = (total_x / sum(total_x)) * 100) %>%
  ungroup()

category_summary


d <-
ggplot(category_summary, 
       aes(x = treatment, 
           y = percentage, 
           fill = category)) +
  geom_col(position = "stack") +  # Stacked bars
  scale_fill_brewer(palette = "Set1") +  # Change to any Brewer palette
  labs(subtitle = "Environmental fate",
       x = "Treatment",
       y = "Proportion (%)",
       fill = "Pesticide Category") +
  theme_minimal()


d

```


# ~ Human health PLI
```{r}

# Summarize total usage by category and treatment
category_summary <- dat %>%
  group_by(treatment, category) %>%  # Group by both treatment and category
  summarise(total_x = sum(PL_HH, na.rm = TRUE), .groups = "drop") %>%
  group_by(treatment) %>%  # Group again by treatment to calculate proportions correctly
  mutate(percentage = (total_x / sum(total_x)) * 100) %>%
  ungroup()

category_summary

e <-
ggplot(category_summary, 
       aes(x = treatment, 
           y = percentage, 
           fill = category)) +
  geom_col(position = "stack") +  # Stacked bars
  scale_fill_brewer(palette = "Set1") +  # Change to any Brewer palette
  labs(subtitle = "Human Health",
       x = "Treatment",
       y = "Proportion (%)",
       fill = "Pesticide Category") +
  theme_minimal()


e

```



# joint plot 


```{r joint plot proportions}

library(ggpubr)

# Modify each plot to rotate x-axis labels
a <- a + theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title = element_blank())
b <- b + theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title = element_blank())
c <- c + theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title = element_blank())
d <- d + theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title = element_blank())
e <- e + theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title = element_blank())

# Arrange the plots with ggarrange
ggarrange(c, d, e, a, b, 
          ncol = 5, 
          nrow = 1, 
          labels = c("A", "B", "C", "D", "E"), 
          common.legend = TRUE, legend = "bottom")

```


```{r}

ggsave(filename = "sym_link_pesticide_data/plots/pesticide_risk_plots/danish_pli_proportion_joint_plot.png",
       width = 9, height = 4.5)

```






